---
title: "Woods Master's Thesis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(readxl)
library(tcltk)
library(ggpubr)
library(plotly)
library(reactable)
theme_set(theme_classic())

setwd("C:/Users/Phil/Dropbox/Thesis- Stretch Activation/Data/Woods - Master's Thesis/Project/Tension + AaBbCc")

my_data <- read_excel("SA-Fatigue_Tension+Step+Kinetics_PW_7-15-22.xlsx", 
                      skip = 5,
                      na="")
phil_awesome_data <-
  my_data %>% 
    dplyr::filter(Exp_Con_Num %in% c(2:6)) %>% 
    dplyr::group_by(Muscle, Exp_Con) %>% 
    dplyr::summarize(n = n(),
                     p0_pre_step_avg = mean(Po_Pre_Step, na.rm=T),
                     p0_pre_step_sd = sd(Po_Pre_Step, na.rm=T),
                     p0_pre_step_se = sd(Po_Pre_Step, na.rm=T)/sqrt(n()),
                     fsa_avg = mean(Fsa, na.rm = T),
                     fsa_sd = sd(Fsa, na.rm = T),
                     fsa_se = sd(Fsa, na.rm = T)/sqrt(n()),
                     fsaf0_avg = mean(FsaF0, na.rm = T),
                     fsaf0_sd = sd(FsaF0, na.rm = T),
                     fsaf0_se = sd(FsaF0, na.rm = T)/sqrt(n()),
                     fsatotal_avg = mean(Fsa_total, na.rm = T),
                     fsatotal_sd = sd(Fsa_total, na.rm = T),
                     fsatotal_se = sd(Fsa_total, na.rm = T)/sqrt(n()),
                     a2_avg = mean(a2, na.rm=T),
                     a2_sd = sd(a2, na.rm = T),
                     a2_se = sd(a2, na.rm = T)/sqrt(n()),
                     r2_avg = mean(r2, na.rm = T),
                     r2_sd = sd(r2, na.rm = T),
                     r2_se = sd(r2, na.rm = T)/sqrt(n()),
                     a3_avg = mean(a3, na.rm=T),
                     a3_sd = sd(a3, na.rm = T),
                     a3_se = sd(a3, na.rm = T)/sqrt(n()),
                     r3_avg = mean(r3, na.rm = T),
                     r3_sd = sd(r3, na.rm = T),
                     r3_se = sd(r3, na.rm = T)/sqrt(n()),
                     a4_avg = mean(a4, na.rm=T),
                     a4_sd = sd(a4, na.rm = T),
                     a4_se = sd(a4, na.rm = T)/sqrt(n()),
                     r4_avg = mean(r4, na.rm = T),
                     r4_sd = sd(r4, na.rm = T),
                     r4_se = sd(r4, na.rm = T)/sqrt(n()),
                     )


## Average plots
(f0_gg <- ggplot(data = phil_awesome_data,
                   aes(x = factor(Exp_Con, 
                                  levels = c("Fat_1", 
                                             "Fat_2", 
                                             "Fat_4.5", 
                                             "Active",
                                             "Active_2")),
                       y = p0_pre_step_avg,
                       color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = p0_pre_step_avg - p0_pre_step_se,
                      ymax = p0_pre_step_avg + p0_pre_step_se,
                      width = 0.1)) +
    ylab("F0") +
   xlab("Experimental Conditions")
  
)

(fsa_gg <- ggplot(data = phil_awesome_data,
                 aes(x = factor(Exp_Con, 
                                levels = c("Fat_1", 
                                           "Fat_2", 
                                           "Fat_4.5", 
                                           "Active",
                                           "Active_2")),
                     y = fsa_avg,
                     color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = fsa_avg - fsa_se,
                      ymax = fsa_avg + fsa_se,
                      width = 0.1)) +
    ylab("Fsa") +
    xlab("Experimental Conditions")
  
)

(fsaf0_gg <- ggplot(data = phil_awesome_data,
                  aes(x = factor(Exp_Con, 
                                 levels = c("Fat_1", 
                                            "Fat_2", 
                                            "Fat_4.5", 
                                            "Active",
                                            "Active_2")),
                      y = fsaf0_avg,
                      color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = fsaf0_avg - fsaf0_se,
                      ymax = fsaf0_avg + fsaf0_se,
                      width = 0.1)) +
    ylab("Fsa/F0") +
    xlab("Experimental Conditions")
  
)

(fsatotal_gg <- ggplot(data = phil_awesome_data,
                    aes(x = factor(Exp_Con, 
                                   levels = c("Fat_1", 
                                              "Fat_2", 
                                              "Fat_4.5", 
                                              "Active",
                                              "Active_2")),
                        y = fsatotal_avg,
                        color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = fsatotal_avg - fsatotal_se,
                      ymax = fsatotal_avg + fsatotal_se,
                      width = 0.1)) +
    ylab("Fsa/(Fsa + F0)") +
    xlab("Experimental Conditions")
  
)
(a2_gg <- ggplot(data = phil_awesome_data,
                 aes(x = factor(Exp_Con, 
                                levels = c("Fat_1", 
                                           "Fat_2", 
                                           "Fat_4.5", 
                                           "Active",
                                           "Active_2")),
                     y = a2_avg,
                     color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = a2_avg - a2_se,
                      ymax = a2_avg + a2_se,
                      width = 0.1)) +
    ylab("a2") +
    xlab("Experimental Conditions")
  
)

(a3_gg <- ggplot(data = phil_awesome_data,
                 aes(x = factor(Exp_Con, 
                                levels = c("Fat_1", 
                                           "Fat_2", 
                                           "Fat_4.5", 
                                           "Active",
                                           "Active_2")),
                     y = a3_avg,
                     color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = a3_avg - a3_se,
                      ymax = a3_avg + a3_se,
                      width = 0.1)) +
    ylab("a3") +
    xlab("Experimental Conditions")
  
)

(a4_gg <- ggplot(data = phil_awesome_data,
                 aes(x = factor(Exp_Con, 
                                levels = c("Fat_1", 
                                           "Fat_2", 
                                           "Fat_4.5", 
                                           "Active",
                                           "Active_2")),
                     y = a4_avg,
                     color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = a4_avg - a4_se,
                      ymax = a4_avg + a4_se,
                      width = 0.1)) +
    ylab("a4") +
    xlab("Experimental Conditions")
  
)

(r2_gg <- ggplot(data = phil_awesome_data,
                       aes(x = factor(Exp_Con, 
                                      levels = c("Fat_1", 
                                                 "Fat_2", 
                                                 "Fat_4.5", 
                                                 "Active",
                                                 "Active_2")),
                           y = r2_avg,
                           color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = r2_avg - r2_se,
                      ymax = r2_avg + r2_se,
                      width = 0.1)) +
    ylab("r2") +
    xlab("Experimental Conditions")
  
)

(r3_gg <- ggplot(data = phil_awesome_data,
                 aes(x = factor(Exp_Con, 
                                levels = c("Fat_1", 
                                           "Fat_2", 
                                           "Fat_4.5", 
                                           "Active",
                                           "Active_2")),
                     y = r3_avg,
                     color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = r3_avg - r3_se,
                      ymax = r3_avg + r3_se,
                      width = 0.1)) +
    ylab("r3") +
    xlab("Experimental Conditions")
  
)

(r4_gg <- ggplot(data = phil_awesome_data,
                 aes(x = factor(Exp_Con, 
                                levels = c("Fat_1", 
                                           "Fat_2", 
                                           "Fat_4.5", 
                                           "Active",
                                           "Active_2")),
                     y = r4_avg,
                     color = Muscle)) +
    geom_point() +
    
    geom_line(aes(group = Muscle)) +
    
    scale_color_manual(breaks = c("soleus", "EDL"),
                       values = c("red", "blue")) +
    geom_errorbar(aes(ymin = r4_avg - r4_se,
                      ymax = r4_avg + r4_se,
                      width = 0.1)) +
    ylab("r4") +
    xlab("Experimental Conditions")
  
)


## Individual fibers plot
my_data2 <- my_data %>% 
  filter(Exp_Con_Num %in% c(2:6))

(f0_plot_fibers <- ggplot(data = my_data2, 
                         aes(x = factor(Exp_Con,
                                        levels = unique(Exp_Con)),
                             y = Po_Pre_Step,
                             color = factor(Mouse),
                             label = fiber_num)) + 
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("F0") +
    facet_wrap( ~ Muscle) 
)

(fsa_plot_fibers <- ggplot(data = my_data2, 
           aes(x = factor(Exp_Con,
                          levels = unique(Exp_Con)),
               y = Fsa,
               color = factor(Mouse),
               label = fiber_num)) +
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("Fsa") +
    facet_wrap( ~ Muscle)
)

(fsaf0_plot_fibers <- ggplot(data = my_data2, 
                           aes(x = factor(Exp_Con,
                                          levels = unique(Exp_Con)),
                               y = FsaF0,
                               color = factor(Mouse),
                               label = fiber_num)) + 
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("Fsa/F0") +
    facet_wrap( ~ Muscle)
)


(fsatotal_plot_fibers <- ggplot(data = my_data2, 
                             aes(x = factor(Exp_Con,
                                            levels = unique(Exp_Con)),
                                 y = Fsa_total,
                                 color = factor(Mouse),
                                 label = fiber_num)) +  
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("Fsa/(Fsa + F0)") +
    facet_wrap( ~ Muscle)
)

(a2_plot_fibers <- ggplot(data = my_data2, 
                          aes(x = factor(Exp_Con,
                                         levels = unique(Exp_Con)),
                              y = a2,
                              color = factor(Mouse),
                              label = fiber_num)) + 
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("a2") +
    facet_wrap( ~ Muscle)
)

(a3_plot_fibers <- ggplot(data = my_data2, 
                          aes(x = factor(Exp_Con,
                                         levels = unique(Exp_Con)),
                              y = a3,
                              color = factor(Mouse),
                              label = fiber_num)) +  
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("a3") +
    facet_wrap( ~ Muscle)
)

(a4_plot_fibers <- ggplot(data = my_data2, 
                          aes(x = factor(Exp_Con,
                                         levels = unique(Exp_Con)),
                              y = a4,
                              color = factor(Mouse),
                              label = fiber_num)) + 
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("a4") +
    facet_wrap( ~ Muscle)
)

(r2_plot_fibers <- ggplot(data = my_data2, 
                                aes(x = factor(Exp_Con,
                                               levels = unique(Exp_Con)),
                                    y = r2,
                                    color = factor(Mouse),
                                    label = fiber_num)) + 
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("r2") +
    facet_wrap( ~ Muscle)
)

(r3_plot_fibers <- ggplot(data = my_data2, 
                          aes(x = factor(Exp_Con,
                                         levels = unique(Exp_Con)),
                              y = r3,
                              color = factor(Mouse),
                              label = fiber_num)) +
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("r3") +
    facet_wrap( ~ Muscle)
)

(r4_plot_fibers <- ggplot(data = my_data2, 
                          aes(x = factor(Exp_Con,
                                         levels = unique(Exp_Con)),
                              y = r4,
                              color = factor(Mouse),
                              label = fiber_num)) +
    geom_point() +
    geom_line(aes(group = fiber_num)) +
    xlab("Experiment Conditions") +
    ylab("r4") +
    facet_wrap( ~ Muscle)
)
```

# Data

## Column {data-width=400, .tabset}

### Raw Data

```{r}
reactable(my_data, groupBy = "Filename")

```
### Avereaged Data
```{r}
reactable(phil_awesome_data)
```

# Stretch Activation

## Column {data-width=500, .tabset}

### F0 - Averaged

```{r}
ggplotly(f0_gg)

```

### Fsa - Averaged

```{r}
ggplotly(fsa_gg)
```

### Fsa/F0 - Averaged

```{r}
ggplotly(fsaf0_gg)
```

### Fsa/(Fsa + F0) - Averaged

```{r}
ggplotly(fsatotal_gg)
```

## Column {data-width=500, .tabset}

### F0 - Individaul Fibers

```{r}
ggplotly(f0_plot_fibers)

```

### Fsa - Individaul Fibers

```{r}
ggplotly(fsa_plot_fibers)
```

### Fsa/F0 - Individaul Fibers

```{r}
ggplotly(fsaf0_plot_fibers)
```

### Fsa/(Fsa + F0) - Individaul Fibers

```{r}
ggplotly(fsatotal_plot_fibers)
```


# Amplitudes

## Column {data-width=500, .tabset}

### a2 - Averaged

```{r, fig.height=5, fig.width=5}
ggplotly(a2_gg)
```

### a3 - Averaged

```{r}
ggplotly(a3_gg)
```

### a4 - Averaged

```{r}
ggplotly(a4_gg)
```

## Column {data-width=500, .tabset}

### a2 - Individual Fibers

```{r, fig.height=5, fig.width=5}
ggplotly(a2_plot_fibers)
```

### a3 - Individual Fibers

```{r}
ggplotly(a3_plot_fibers)
```

### a4 - Individual Fibers

```{r}
ggplotly(a4_plot_fibers)
```


# Rates

## Column {data-width=500, .tabset}

### r2 - Averaged

```{r, fig.height=5, fig.width=5}
ggplotly(r2_gg)
```

### r3 - Averaged

```{r}
ggplotly(r3_gg)
```

### r4 - Averaged

```{r}
ggplotly(r4_gg)
```

## Column {data-width=500, .tabset}

### r2 - Individual Fibers

```{r, fig.height=5, fig.width=5}
ggplotly(r2_plot_fibers)
```

### r3 - Individual Fibers

```{r}
ggplotly(r3_plot_fibers)
```

### r4 - Individual Fibers

```{r}
ggplotly(r4_plot_fibers)
```
