Code example for Brent

This is just reading in packages. 
  Tidyverse helps with wrangling and filtering data 
  Everything else is important for analysis
  
```{r}
library(tidyverse)
library(pbkrtest)
library(multcomp)
library(emmeans)
```
Reading in Data
```{r}
my_data = readxl::read_excel(file.choose(),
                     sheet = "Manuscript.2",
                     skip = 5,
                     na="") 

my_data = my_data %>% 
  filter(Exp_Con_Num %in% c(2:4)) %>% 
  filter(fiber_type_num %in% c(1:4))
```

How to conduct repeated measures linear mixed model with dependent variable (Po_Post_Step) and two independent variables (Exp_Con) and (fiber_type) (NO INTERACTION). To make in repeated measures, the inclusion of "as.factor(Exp_Con) is needed.

```{r}
(force_mdl = lmer(Po_Post_Step ~ Exp_Con + fiber_type + (1 + as.factor(Exp_Con) |Mouse), data = my_data))

```
```{r}
anova(force_mdl)
```
```{r}
emmeans(force_mdl, list(pairwise ~ Exp_Con + fiber_type), adjust = "tukey")
```

How to conduct repeated measures linear mixed model with dependent variable (Po_Post_Step) and two independent variables (Exp_Con) and (fiber_type) to CHECK FOR INTERACTION. Interactions in R is simply as changing a '+' to a '*' in R. This is not repeated measures, however you can simply add the above code to make it so.

```{r}
(force_int_mdl = lmer(Po_Post_Step ~ Exp_Con * fiber_type + (1|Mouse), data = my_data))
```
```{r}
anova(force_int_mdl)
```
```{r}
emmeans(force_int_mdl, list(pairwise ~ Exp_Con + fiber_type), adjust = "tukey")
```

